\dppTitle

### 2014-03-06 manuscripts/dpp-msbayes/dpp-msbayes-figures.tex
Adding bmc-style figure titles to dpp ms.
Adding bmc-style figure titles to `dpp-msbayes-figure.tex` enclosed
withing `ifbmc` statements.

%% Validation model choice
\mFigure{../../validation/images/validation-model-choice-psi.pdf}{
    \validationModelChoiceComparisonCaption{unadjusted}{$\divTimeNum = 1$}
}{figValidationModelChoicePsi}

\mFigure{../../validation/images/validation-model-choice-omega.pdf}{
    \validationModelChoiceComparisonCaption{unadjusted}{$\divTimeDispersion < 0.01$}
}{figValidationModelChoiceOmega}

%% Power results
\mFigure{../../power-comparison/images/old-power-psi-4.pdf}{
    \powerCommentSummary{\powerSeriesOld}
    \powerPsiComment{\powerSeriesOld}
    \timeConversionComment
    Four of the six data-generating models of the \powerSeriesOld series
    are shown;
    please see Figure~S\ref{figPowerPsiOld} for all results.
}{figPowerPsiOld4}

\mFigure{../../power-comparison/images/old-power-omega-4.pdf}{
    \powerCommentSummary{\powerSeriesOld}
    \powerDispersionComment{\powerSeriesOld}
    \timeConversionComment
    Four of the six data-generating models of the \powerSeriesOld series
    are shown;
    please see Figure~S\ref{figPowerPsiOld} for all results.
}{figPowerOmegaOld4}

\mFigure{../../power-comparison/images/old-power-psi-prob-4.pdf}{
    \powerSupportCommentSummary{\powerSeriesOld}
    \powerProbComment{$p(\divTimeNum = 1 | \ssSpace)$}{\powerSeriesOld}
    \timeConversionComment
    Four of the six data-generating models of the \powerSeriesOld series
    are shown;
    please see Figure~S\ref{figPowerPsiOld} for all results.
}{figPowerPsiProbOld4}

\mFigure{../../power-comparison/images/old-power-omega-prob-4.pdf}{
    \powerSupportCommentSummary{\powerSeriesOld}
    \powerProbComment{$p(\divTimeDispersion < 0.01 | \ssSpace)$}{\powerSeriesOld}
    \timeConversionComment
    Four of the six data-generating models of the \powerSeriesOld series
    are shown;
    please see Figure~S\ref{figPowerPsiOld} for all results.
}{figPowerOmegaProbOld4}

%% Empirical results
\mFigure{../../empirical-analyses/plots/philippines-psi.pdf}{
    The (A--E) posterior and (F--J) prior probabilities of the number of
    divergence events (\divTimeNum) when the data of the 22 pairs of taxa from
    the Philippines are analyzed under the five models indicated at the top of
    each column of plots (Table~\ref{tabEmpiricalModels}).
    The average prior probability of an (K--O) unordered and (P--T)
    ordered model of divergence (\divTimeIndexVector) with \divTimeNum
    divergence-time parameters is also shown.
    The posterior median of the dispersion index of divergence times
    (\divTimeDispersion) is also given for each model, followed by the 95\%
    highest posterior density interval in parantheses.
}{figPhilippines}

\widthFigure{0.4}{../../empirical-analyses/plots/negros-panay-psi.pdf}{listformat=figList}{
    The posterior probabilities of the number of divergence events,
    \divTimeNum, when the data of the 9 pairs of taxa from Negros and Panay
    Islands are analyzed under the DPP model that samples over (A) unordered
    and (B) ordered models of divergence (Table~\ref{tabEmpiricalModels}).
    Both models share the same (C) prior probability of the number of
    divergence events, and the average prior probability of an (D)
    unordered and (E) ordered model of divergence (\divTimeIndexVector) with
    \divTimeNum divergence-time parameters.
    The posterior median of the dispersion index of divergence times
    (\divTimeDispersion) is also given for each model, followed by the 95\%
    highest posterior density interval in parantheses.
}{figNegrosPanay}
\clearpage

>>>>

%% Validation model choice
\mFigure{../../validation/images/validation-model-choice-psi.pdf}{%
    \ifbmc{\csentence{Comparison of model-choice behavior.}}{}
    \validationModelChoiceComparisonCaption{unadjusted}{$\divTimeNum = 1$}
}{figValidationModelChoicePsi}

\mFigure{../../validation/images/validation-model-choice-omega.pdf}{
    \ifbmc{\csentence{Comparison of model-choice behavior.}}{}
    \validationModelChoiceComparisonCaption{unadjusted}{$\divTimeDispersion < 0.01$}
}{figValidationModelChoiceOmega}

%% Power results
\mFigure{../../power-comparison/images/old-power-psi-4.pdf}{
    \ifbmc{\csentence{Power comparison.}}{}
    \powerCommentSummary{\powerSeriesOld}
    \powerPsiComment{\powerSeriesOld}
    \timeConversionComment
    Four of the six data-generating models of the \powerSeriesOld series
    are shown;
    please see Figure~S\ref{figPowerPsiOld} for all results.
}{figPowerPsiOld4}

\mFigure{../../power-comparison/images/old-power-omega-4.pdf}{
    \ifbmc{\csentence{Power comparison.}}{}
    \powerCommentSummary{\powerSeriesOld}
    \powerDispersionComment{\powerSeriesOld}
    \timeConversionComment
    Four of the six data-generating models of the \powerSeriesOld series
    are shown;
    please see Figure~S\ref{figPowerPsiOld} for all results.
}{figPowerOmegaOld4}

\mFigure{../../power-comparison/images/old-power-psi-prob-4.pdf}{
    \ifbmc{\csentence{Power comparison.}}{}
    \powerSupportCommentSummary{\powerSeriesOld}
    \powerProbComment{$p(\divTimeNum = 1 | \ssSpace)$}{\powerSeriesOld}
    \timeConversionComment
    Four of the six data-generating models of the \powerSeriesOld series
    are shown;
    please see Figure~S\ref{figPowerPsiOld} for all results.
}{figPowerPsiProbOld4}

\mFigure{../../power-comparison/images/old-power-omega-prob-4.pdf}{
    \ifbmc{\csentence{Power comparison.}}{}
    \powerSupportCommentSummary{\powerSeriesOld}
    \powerProbComment{$p(\divTimeDispersion < 0.01 | \ssSpace)$}{\powerSeriesOld}
    \timeConversionComment
    Four of the six data-generating models of the \powerSeriesOld series
    are shown;
    please see Figure~S\ref{figPowerPsiOld} for all results.
}{figPowerOmegaProbOld4}

%% Empirical results
\mFigure{../../empirical-analyses/plots/philippines-psi.pdf}{
    \ifbmc{\csentence{Empirical results for 22 Philippine taxa.}}{}
    The (A--E) posterior and (F--J) prior probabilities of the number of
    divergence events (\divTimeNum) when the data of the 22 pairs of taxa from
    the Philippines are analyzed under the five models indicated at the top of
    each column of plots (Table~\ref{tabEmpiricalModels}).
    The average prior probability of an (K--O) unordered and (P--T)
    ordered model of divergence (\divTimeIndexVector) with \divTimeNum
    divergence-time parameters is also shown.
    The posterior median of the dispersion index of divergence times
    (\divTimeDispersion) is also given for each model, followed by the 95\%
    highest posterior density interval in parantheses.
}{figPhilippines}

\widthFigure{0.4}{../../empirical-analyses/plots/negros-panay-psi.pdf}{listformat=figList}{
    \ifbmc{\csentence{Empirical results for 9 Philippine taxa.}}{}
    The posterior probabilities of the number of divergence events,
    \divTimeNum, when the data of the 9 pairs of taxa from Negros and Panay
    Islands are analyzed under the DPP model that samples over (A) unordered
    and (B) ordered models of divergence (Table~\ref{tabEmpiricalModels}).
    Both models share the same (C) prior probability of the number of
    divergence events, and the average prior probability of an (D)
    unordered and (E) ordered model of divergence (\divTimeIndexVector) with
    \divTimeNum divergence-time parameters.
    The posterior median of the dispersion index of divergence times
    (\divTimeDispersion) is also given for each model, followed by the 95\%
    highest posterior density interval in parantheses.
}{figNegrosPanay}
\clearpage
